---
title: "Using SPRING254753nguy0700"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using SPRING254753nguy0700}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "figures/",
  dev = "png"
)
library(SPRING254753nguy0700)
```

# Introduction

This vignette introduces the R package `SPRING254753nguy0700`, which provides tools for bootstrapping, normal curve visualization, beta distribution estimation, and simple sampling. Below we demonstrate the four main functions and the included dataset.

# Example Dataset

This package includes a dataset called `fire`. Here's how it looks:

```{r}
head(fire)
```

# Function 1: `myboot2()`

This function performs bootstrapping on a numeric vector using a user-defined statistic.

```{r}
set.seed(1)
x <- rnorm(100)
x <- rnorm(100)
boot_means <- myboot2(x, mean, nboot = 1000)

# Make sure it's numeric
if (is.numeric(boot_means)) {
  hist(boot_means, main = "Bootstrapped Means", xlab = "Mean", col = "skyblue")
} else {
  print("boot_means is not numeric")
}

```

# Function 2: `myncurve()`

This function visualizes a normal curve and highlights the area to the left of a specific value.

```{r}
myncurve(mu = 10, sigma = 2, a = 10)

```

# Function 3: `estimate_beta_mle()`

This function estimates the parameters of a beta distribution via maximum likelihood.

```{r}
beta_sample <- rbeta(100, 2, 5)
alpha_vals <- seq(1, 5, length.out = 100)
beta_vals <- seq(1, 5, length.out = 100)
result <- estimate_beta_mle(beta_sample, alpha = alpha_vals, beta = beta_vals)

# Only print the MLE results
list(
  max_alpha = result$maxalpha,
  max_beta = result$maxbeta,
  log_likelihood = log(result$maxl)
)


```

# Function 4: `mysample()`

This function takes a sample and returns its mean, standard deviation, and histogram.

```{r}
mysample(n = 1000, iter = 1, time = 0)


```

# Conclusion

This vignette demonstrated how to use the four key functions in `SPRING254753nguy0700` with both simulated and included data. The package provides an easy way to explore basic statistical procedures like bootstrapping and MLE estimation.
